### 2023-05-29 paper/Chapters/Chapter1.tex
WIP on paper

Typically, camera calibration is obtained by capturing an image of a known
calibration pattern, which is then used to estimate the camera parameters.
Alternatively, some methods do not use a calibration pattern but instead infer
geometric constraints directly from the scene. However, this approach is
generally less accurate.

@@

This additional points will further constrain the camera calibration, improving
the accuracy of the calibration parameters.

\begin{figure}
	\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=4,size=3cm, connect spies}]
		\node[anchor=south west,inner sep=0] (image) at (0,0)
    % {\includegraphics[width=0.6\textwidth]{distorted_image}};
    {\includegraphics[width=0.8\textwidth]{distorted_image}};
		\begin{scope}[x={(image.south east)},y={(image.north west)}]
			\spy[red] on (3.3,1.7) in node [left] at (10.1,1.7);
			\spy[blue] on (4.6,3.2) in node [right] at (8.1,5.3);
		\end{scope}
	\end{tikzpicture}
  \caption{Example of corners near the center of the image and near the edge}
\end{figure}

@@

This paper has the following structure: in \autoref{sec:related_work}, we will describe the related work, including the
literature search method and methodology, various subtopics of the camera
calibration, mention conjugate translations, and outline the state-of-the-art
solutions. We define the research gap in \autoref{sec:gap_analysis} and outline
the proposed approach to solution and evaluation in
\autoref{sec:problem_setting_and_approach_to_solution}. We will describe the
early results in \autoref{sec:early_results_and_discussion}, including the
dataset analysis, feature detector, and conjugately translated points simulator.
In \autoref{sec:summary_and_future_work}, we will summarize the results and
outline future work.
\todo{Update}

\endinput

>>>>

Typically, camera calibration is obtained by capturing an image of a known
calibration pattern, which is then used to estimate the camera parameters.
Alternatively, some methods do not use a calibration pattern but instead, infer
geometric constraints directly from the scene. However, this approach is
generally less accurate.

@@

These additional points will further constrain the camera calibration, improving
the accuracy of the calibration parameters.

\begin{figure}
	\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=4,size=3cm, connect spies}]
		\node[anchor=south west,inner sep=0] (image) at (0,0)
		% {\includegraphics[width=0.6\textwidth]{distorted_image}};
		{\includegraphics[width=0.8\textwidth]{distorted_image}};
		\begin{scope}[x={(image.south east)},y={(image.north west)}]
			\spy[red] on (3.3,1.7) in node [left] at (10.1,1.7);
			\spy[blue] on (4.6,3.2) in node [right] at (8.1,5.3);
		\end{scope}
	\end{tikzpicture}
	\caption{Example of corners near the center of the image and the edge}
\end{figure}

@@

This paper has the following structure: in \autoref{sec:related_work}, we will describe the related work, including the
literature search method and methodology, various subtopics of the camera
calibration, mention conjugate translations, and outline the state-of-the-art
solutions. We define the research gap in \autoref{sec:gap_analysis} and outline
the proposed approach to solution and evaluation in
\autoref{sec:problem_setting_and_approach_to_solution}. We will describe the
early results in \autoref{sec:early_results_and_discussion}, including the
dataset analysis, feature detector, and conjugately translated points simulator.
In \autoref{sec:summary_and_future_work}, we will summarize the results and
outline future work.
\todo{Update}
\todo{add the link to the repo}

### 2023-05-29 paper/Chapters/Chapter2.tex
WIP on paper

The detection of the calibration board's features is a crucial step in the
camera calibration pipeline. The detection accuracy directly affects the
calibration accuracy. Besides the feature detection, it's also important to
associate the detected features with the board's corners.

There are various of the feature detection methods. Many of them require
prior knowledge of the board's geometry, such as the number of rows and columns,
and require the full visibility of the board. For example, the default OpenCV
implementation of the chessboard detection~\citep{OpenCVCameraCalibration}.

Because of that, other methods were proposed, such as
\cite{fuersattelOCPADOccludedCheckerboard2016} and
\cite{geigerAutomaticCameraRange2012}. Those method can detect the board and
associate the corners with the borders' corners under
the partial occlusion and do not require prior knowledge of the board's geometry.

>>>>

The detection of the calibration board's features is a crucial step in the
camera calibration pipeline. The detection accuracy directly affects the
calibration accuracy. Besides feature detection, it's also important to
associate the detected features with the board's corners.

There are various feature detection methods. Many of them require
prior knowledge of the board's geometry, such as the number of rows and columns,
and require the full visibility of the board. For example, the default OpenCV
implementation of the chessboard detection~\citep{OpenCVCameraCalibration}.

Because of that, other methods were proposed, such as
\cite{fuersattelOCPADOccludedCheckerboard2016} and
\cite{geigerAutomaticCameraRange2012}. Those methods can detect the board and
associate the corners with the borders' corners under
the partial occlusion and do not require prior knowledge of the board's geometry.

### 2023-05-29 paper/Chapters/Chapter4.tex
WIP paper
WIP on paper

For the feature detection, we used the approach, proposed by
\cite{geigerAutomaticCameraRange2012} (see \cref{sec:boards_features_detection,
	sec:feature_detection}).

@@

In this work, we obtained the camera calibration in two steps: first, we
used the approach, proposed by \cite{scaramuzzaToolboxEasilyCalibrating2006} to
obtain the initial approximation of the camera parameters. Then, we used the
optimization to minimize the reprojection error between the board and the
back-projected corners. A division model is very powerful, and is able to
express a wide number of range of distortions
\citep{prittsMinimalSolversRectifying2021}. In this work, we used a model with
two parameters to allow for a better flexibility during the optimization.

@@

In this work, we focused on the single image, while the original approach relied
on the multiple images. Therefore, we used only the first two steps of the
algorithm.

@@

Lastly, to select the correct \(H\), the author assumes that one of the boards'
corners has the coordinates \( \begin{pmatrix}
	0, 0
\end{pmatrix}^{T}\). Then, the rotation wouldn't affect this
point, and it would be projected to   \(\begin{pmatrix}
	t_1, t_2
\end{pmatrix}^{T}\). Hence, the best matrix would be such that has the closest
\(\begin{pmatrix}
	t_1, t_2
\end{pmatrix}^{T}\) to \(\begin{pmatrix}
	X, Y
\end{pmatrix}^{T}\) of the corner, which is associated with the board's corner
with corrdinates \(\begin{pmatrix}
	0, 0
\end{pmatrix}^{T}\).

However, often the algorithm finds who matrices \(H\) such that they have the
same \(t_1\) and \(t_2 \), but different \(r_{11}\), \(r_{12}\), \(r_{21}\). To
find the best matrix, we found the intrinsic values for each of them, and
backprojected the board's corners using both matrices.
Then, we used the one which gave the smallest reprojection error.

@@

The model converged to the same results compared to the initial parameters, set
using the Scaramuzza solver, unless the initial guess was very degenerate (i.e.
\(R\) was such that the board plane passed through the principal point, and all
backprojected points were projected onto the same line).

This issue also occured with random small initial values, due to the best
approximation for \(R\) which minimizes \(L\) when the distance from the
back-projected board from the measure one was high (i.e., the \(t\) was far from
the true value) being the degenerate solution\todo{Am I using the term
	correctly?}. In order to avoid this issue, we first optimized only the \(t\),
until the loss function converged, meaning that \(t\) is close to the true
value.

However, another issue was that when the board was rotated close to the
\(180^{\circ}\), \(R\) once again converged to the degenerate solution. In order
to avoid this issue, we found the solution with initial \(\theta_z\) set to
value, close to \(0^{\circ}\) and \(180^{\circ}\), and then used the solution
which minimized the loss function.

@@

Often, not all of the board's corners were detected initially. Firstly, we
assumed that the whole board was detected, and imputed the missing points in the
board space.\todo{Add ref to the figure}. Then, we tried extending the board
points.

@@

For each of the detected corners on all images, we collected the values of the
response function at the previously detected corners, and around them.
We didn't collect the values of all of the pixels, in order to reduce the number
of very simple examples.

@@

We used both of the approaches to train the classifier, and compared the
results in \cref{sec:classification}.

>>>>

For feature detection, we used the approach, proposed by
\cite{geigerAutomaticCameraRange2012} (see \cref{sec:boards_features_detection,
	sec:feature_detection}).

@@

In this work, we obtained the camera calibration in two steps: first, we
used the approach, proposed by \cite{scaramuzzaToolboxEasilyCalibrating2006} to
obtain the initial approximation of the camera parameters. Then, we used 
optimization to minimize the reprojection error between the board and the
back-projected corners. A division model is very powerful and can
express a wide range of distortions
\citep{prittsMinimalSolversRectifying2021}. In this work, we used a model with
two parameters to allow for better flexibility during the optimization.

@@

In this work, we focused on a single image, while the original approach relied
on multiple images. Therefore, we used only the first two steps of the
algorithm.

@@

Lastly, to select the correct \(H\), the author assumes that one of the boards'
corners has the coordinates \( \begin{pmatrix}
	0, 0
\end{pmatrix}^{T}\). Then, the rotation wouldn't affect this
point, and it would be projected to   \(\begin{pmatrix}
	t_1, t_2
\end{pmatrix}^{T}\). Hence, the best matrix would be such that has the closest
\(\begin{pmatrix}
	t_1, t_2
\end{pmatrix}^{T}\) to \(\begin{pmatrix}
	X, Y
\end{pmatrix}^{T}\) of the corner, which is associated with the board's corner
with coordinates \(\begin{pmatrix}
	0, 0
\end{pmatrix}^{T}\).

However, often the algorithm finds who matrices \(H\) such that they have the
same \(t_1\) and \(t_2 \), but different \(r_{11}\), \(r_{12}\), \(r_{21}\). To
find the best matrix, we found the intrinsic values for each of them and
back-projected the board's corners using both matrices.
Then, we used the one which gave the smallest reprojection error.

@@

The model converged to the same results compared to the initial parameters, set
using the Scaramuzza solver, unless the initial guess was very degenerate (i.e.
\(R\) was such that the board plane passed through the principal point and all
back-projected points were projected onto the same line).

This issue also occurred with random small initial values, due to the best
approximation for \(R\) which minimizes \(L\) when the distance from the
back-projected board from measure one was high (i.e., the \(t\) was far from
the true value) being the degenerate solution\todo{Am I using the term
	correctly?}. To avoid this issue, we first optimized only the \(t\),
until the loss function converged, meaning that \(t\) is close to the true
value.

However, another issue was that when the board was rotated close to the
\(180^{\circ}\), \(R\) once again converged to the degenerate solution. In order
to avoid this issue, we found the solution with the initial \(\theta_z\) set to
value, close to \(0^{\circ}\) and \(180^{\circ}\), and then used the solution
which minimized the loss function.

@@

Often, not all of the board's corners were detected initially. Firstly, we
assumed that the whole board was detected, and imputed the missing points in the
board space \cref{fig:extended_board_img}. Then, we tried extending the board
points.

@@

For each of the detected corners on all images, we collected the values of the
response function at the previously detected corners, and around them.
We didn't collect the values of all of the pixels, to reduce the number
of very simple examples.

@@

We used both approaches to train the classifier and compared the
results in \cref{sec:classification}.

### 2023-05-29 paper/Chapters/Chapter5.tex
WIP on paper

We created a symulator to generate distorted points as described in
\cref{sub:complete_projection_and_backprojection}. We used it to test the
solver, and test the correctness of projection and back-projection points.

@@

\begin{itemize}
	\item Reprojection error
	\item Number of detected corners
\end{itemize}

@@

For this project, we required a highly distorted dataset of chessboard images.
We collected a number of datasets, but the feature detector we used supports
detecting only the boards with the constant tile size, therefore we cannot use
AprilGrid nor CharuCO boards. The feature detector is the only limiting factor.

@@

\textcite{duisterhofTartanCalibIterativeWideAngle2022} also provide their
dataset from the TartanCalib project. Currently, the dataset contains only
AprilGrid patterns, as the toolchain doesn't support chessboard.

@@

\begin{minipage}{0.5\linewidth}
	In order to get accurate predictions for the possibly missing points, we need
	very accurate camera calibration. We used the reprojection error as a metric
	for the calibration quality.
	In order to calculate the reprojection error, we have to perform the
	rootfinding \cref{subsub:back_projection_using_the_division_model}. We assume
	that all of the points lay within the image, or they get out of the borders
	a little bit (we use the constant \(1.1\) of the maximum radius). If the
	camera calibration is poor, the rootfinding might fail. On the initial
	calibration the number of the failed rootfindings was much higher.
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
	\resizebox{\linewidth}{!}{
		\begin{tikzpicture}
			\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
				115/Correctly detected,
				80/Reprojection error > 10,
				254/Not correctly detected
			}
		\end{tikzpicture}
	}
	\captionsetup{width=.9\linewidth}
	\captionof{figure}{Initial calibration}
	\resizebox{\linewidth}{!}{
		\begin{tikzpicture}
			\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
				658/Correctly detected,
				19/Reprojection error > 10,
				115/Not correctly detected
			}
		\end{tikzpicture}
	}
	\captionsetup{width=.9\linewidth}
	\captionof{figure}{Final calibration}
\end{minipage}

\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}[
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Initial calibration}
			]
			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/reprojection_error_init.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Initial calibration's reprojection error histogram}
\end{figure}
\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}[
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Reprojection error}
			]
			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/reprojection_error_final.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Final calibration's reprojection error histogram}
\end{figure}

@@

>>>>

We created a simulator to generate distorted points as described in
\cref{sub:complete_projection_and_backprojection}. We used it to test the
solver and test the correctness of projection and back-projection points.
However, since the simulator used the same camera model as the solver, the
initial camera calibration was perfect.

@@

As noted by \cite{duisterhofTartanCalibIterativeWideAngle2022}, the evaluation
of the camera calibration is not straightforward. No ground truth exists for
feature detection or camera calibration.

Typically, the reprojection error is used as a metric for the camera
calibration, but it depends on multiple factors: type of the calibration
pattern, the camera model, and the types of the lens.

Also, by using more features, we can get better calibration, as we have more
constraints, but the reprojection error might be higher.

As currently the algorithm only supports processing a single checkerboard, we
cannot compare to \cite{duisterhofTartanCalibIterativeWideAngle2022}, which uses
AprilTags, nor to the \cite{lochmanBabelCalibUniversalApproach2021}, who
provides the detected corners for all of the boards.
\todo{Should I maybe tell less about it?}

Because of that, we instead artificially removed some of the points from the
detections, to ensure that we can recover them. We also created
artificially occluded points by overlaying a separate image, as it poses
problems for the feature detector.

Lastly, we evaluated the newly detected points on real-world datasets.

@@

For this project, we required a highly distorted dataset of chessboard images.
We collected several datasets, but the feature detector we used supports
detecting only the boards with the constant tile size, therefore we cannot use
AprilGrid nor CharuCO boards. The feature detector is the only limiting factor.

@@

\textcite{duisterhofTartanCalibIterativeWideAngle2022} also provide their
dataset from the TartanCalib project. Currently, the dataset contains only
AprilGrid patterns, as the toolchain doesn't support a chessboard.

@@

\begin{minipage}{0.5\linewidth}
	To get accurate predictions for the possibly missing points, we need
	very accurate camera calibration. We used the reprojection error as a metric
	for the calibration quality.
	To calculate the reprojection error, we have to perform the
	rootfinding \cref{subsub:back_projection_using_the_division_model}. We assume
	that all of the points lay within the image, or they get out of the borders
	a little bit (we use the constant \(1.1\) of the maximum radius). If the
	camera calibration is poor, the root-finding might fail. On the initial
	calibration the number of the failed root-findings was much higher.
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
	\resizebox{\linewidth}{!}{
		\begin{tikzpicture}
			\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
				115/Correctly detected,
				80/Reprojection error > 10,
				254/Not correctly detected
			}
		\end{tikzpicture}
	}
	\captionsetup{width=.9\linewidth}
	\captionof{figure}{Initial calibration}
	\resizebox{\linewidth}{!}{
		\begin{tikzpicture}
			\pie[rotate=90, explode=0.1, sum=auto, color={green!60, blue!60, red!60}, text=legend]{
				658/Correctly detected,
				19/Reprojection error > 10,
				115/Not correctly detected
			}
		\end{tikzpicture}
	}
	\captionsetup{width=.9\linewidth}
	\captionof{figure}{Final calibration}
\end{minipage}

% \begin{figure}[h]
% 	\begin{tikzpicture}
% 		\begin{axis}[
% 				ybar interval,
% 				ymin=0,
% 				ylabel={Frequency},
% 				xlabel={Value},
% 				height=0.3\linewidth,
% 				width=\linewidth,
% 				ticklabel style = {font=\tiny},
% 				% title={Initial calibration}
% 			]
% 			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
% 				% \addplot+ [hist={bins=30}] table [y index=0]
% 				{data/reprojection_error_init.txt};
% 		\end{axis}
% 	\end{tikzpicture}
% 	\caption{Initial calibration's reprojection error histogram}
% \end{figure}
% \begin{figure}[h]
% 	\begin{tikzpicture}
% 		\begin{axis}[
% 				ybar interval,
% 				ymin=0,
% 				ylabel={Frequency},
% 				xlabel={Value},
% 				height=0.3\linewidth,
% 				width=\linewidth,
% 				ticklabel style = {font=\tiny},
% 				% title={Reprojection error}
% 			]
% 			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
% 				% \addplot+ [hist={bins=30}] table [y index=0]
% 				{data/reprojection_error_final.txt};
% 		\end{axis}
% 	\end{tikzpicture}
% 	\caption{Final calibration's reprojection error histogram}
% \end{figure}
\todo{Add data and enable}

@@

\subsection{Recovery of artificially removed points}\label{sub:recovery_of_artificially_removed_points}

We removed 20\% of the points from the original board, and then tried to recover
them.

\begin{figure}
  \includegraphics[width=\linewidth]{refined_pruned_corners.png}
  \caption{Recovered occluded points}
\end{figure}

\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}[
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Initial calibration}
			]
			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/pruned_number_of_features.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Initial calibration's reprojection error histogram}
\end{figure}
\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}[
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Reprojection error}
			]
			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/recovered_pruned_number_of_features.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Final calibration's reprojection error histogram}
\end{figure}

\subsection{Performance under occlusion}\label{sub:performance_under_occlusion}

Occlusions pose additional complications for the feature detection. We added an
image on top of the board, and tried to recover additional points. Often the
initial feature detector failed to detect points near the occlusion.

\begin{figure}
  \includegraphics[width=\linewidth]{refined_overlayed_corners.png}
  \caption{Recovered occluded points}
\end{figure}

\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}[
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Initial calibration}
			]
			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/occluded_number_of_features.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Initial calibration's reprojection error histogram}
\end{figure}
\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}[
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Reprojection error}
			]
			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/recovered_occluded_number_of_features.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Final calibration's reprojection error histogram}
\end{figure}

\subsection{Recovery of previously undetected points}\label{sub:recovery_of_previously_undetected_points}

### 2023-05-29 paper/paper.tex
WIP on paper

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
openany
]{MastersDoctoralThesis} % The class file specifying the document structure

@@

	Current state-of-the-art techniques occasionally fail to accurately estimate
	the camera parameters for wide-angle lenses, as most of the algorithms assume
	lens with medium to small distortion. Partially it occurs due to extreme
	distortion at the edges of the image, which poses additional challenges to
	feature detection algorithms. We propose a novel approach for detecting
	additional features on the imaged calibration pattern using intermediate
	camera calibration. Utilizing the prior information about the calibration
	pattern's geometry, we can estimate the possible positions of the previously
	undetected features. Those features are filtered using the binary classifier,
	and the remaining ones are used to further constrain the camera calibration.
	The proposed method consists of three key steps: \((1)\) feature
	detection and estimation of the lattice geometry, \((2)\) initial camera
	calibration by solving the two-steps linear minimization problem, and \((3)\)
	estimation the possible positions of the undetected features by projecting the
	imputed and extended lattice geometry onto the image plane, and filtering them
	using the binary classifier.

>>>>

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
% draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
openany
]{MastersDoctoralThesis} % The class file specifying the document structure

@@

	Current state-of-the-art techniques occasionally fail to accurately estimate
	the camera parameters for wide-angle lenses, as most of the algorithms assume
	lenses with medium to small distortion. Partially it occurs due to extreme
	distortion at the edges of the image, which poses additional challenges to
	feature detection algorithms. We propose a novel approach for detecting
	additional features on the imaged calibration pattern using intermediate
	camera calibration. Utilizing the prior information about the calibration
	pattern's geometry, we can estimate the possible positions of the previously
	undetected features. Those features are filtered using the binary classifier,
	and the remaining ones are used to further constrain the camera calibration.
	The proposed method consists of three key steps: \((1)\) feature
	detection and estimation of the lattice geometry, \((2)\) initial camera
	calibration by solving the two-steps linear minimization problem, and \((3)\)
	estimation the possible positions of the undetected features by projecting the
	imputed and extended lattice geometry onto the image plane, and filtering them
	using the binary classifier.
